\section{Discussion}

Subjects performed best with green and red lights. While these differences
may appear too small to be meaningful, at $35$ mph, a car travels $51$ feet per
second. A difference of $.1$s translates to over $5$ ft traveled, which could
be extremely significant for whatever is in those $5$ ft.  Further analysis
of the data shows that there was also a meaningful difference in the spread
of reaction times. While the means were quite similar, different colors had
a higher proportion of slow-responding outliers. The misses (marked in X's
in TODO Fig. 2) also represent dramatic differences in visibility, as some
lights tended to disappear into the background of similarly colored
distractors.  There are a range of factors that may influence why different
colors performed differently. We must acknowledge the possibility that our
backgrounds (which were varied, but by no means randomly created or chosen)
might favor certain colors in a way that is not representative of driving
experience. Additionally, this is by no means a perfectly controlled
situation, and a whole range of confounding factors could be influencing
the results.  One question we had initially was whether red was a proper
choice for bike tail lights. By convention, bike tail lights match cars'
red lights. It seemed possible then that the low signal to noise ration
could make red more difficult to spot. However, this was not the case. It
seems likely that in driving environments, we are particularly attentive to
lights of certain colors (green and red lights have particular meaning, and
red lights are the steady signal for the objects we tend to look for). This
could certainly compensate for the effects of noise. Similarly, pink,
white, blue, and cyan lights rarely have relevance when driving. Obviously,
this is speculation, but it is reassuring to know that our tail light
conventions aren't necessarily making us less safe.  One of the initial
motivations for this study was to understand what factors make bikers more
visible. In researching prior work, we came across a study showing that
reflective clothing, especially on the legs, improves visibility far more
than bikers predict \cite{wood2013bicyclists}. In preparing the experiment, we found
that the cyclist's body was a far more salient stimulus (popping out so
strongly that it requiring significant modification to make the
comparatively small light source a factor.) Thus cyclists interested in
visibility should perhaps worry less about tail light color, and instead
add reflective clothing to make their body more visible.

